---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
<!-- badges: start -->
[![Travis build status](https://travis-ci.org/news-r/newsr.svg?branch=master)](https://travis-ci.org/news-r/newsr)
<!-- badges: end -->

# newsr

All of news-r _R_ tools in one place.

## Packages

Lists of packages included.

### Data

Data-related packages, packages to collect data, generally from APIs.

- [newsapi](https://github.com/news-r/newsapi) - newsapi.org (news aggregator)
- [guardian](https://github.com/news-r/guardian) - The Guardian API
- [papers](https://github.com/news-r/papers) - Information on newspapers
- [loc](https://github.com/news-r/loc) - Library of Congress API
- [webhoser](https://github.com/news-r/webhoser) - webhose.io API (news aggregator)
- [currents](https://github.com/news-r/currents) - Currents API (news aggregator)
- [nytimes](https://github.com/news-r/nytimes) - New York Times API
- [spotlight](https://github.com/news-r/spotlight) - Entity extraction with DBPedia Spotlight
- [stocknews](https://github.com/news-r/stocknews) - Stocknews API (financial news)
- [ft](https://github.com/news-r/ft) - Financial Times API
- [accunews](https://github.com/news-r/accunews) - AccuNews API (local news)
- [newsriver](https://github.com/news-r/newsriver) - newsriver.io API (news aggregator)
- [hoaxy](https://github.com/news-r/hoaxy) - Fake news monitoring
- [factcheck](https://github.com/news-r/factcheck) - Fact check queries or publishers
- [letterbox](https://github.com/news-r/letterbox) - News article crawler

### Analysis

Packages for analysis, generally text mining.

- [textanalysis](https://github.com/news-r/textanalysis) - Broad text analysis in R
- [gensimr](https://gensimr.news-r.org) - Topic Modeling
- [word2vec.r](https://word2vec.news-r.org) - Word2Vec embeddings in R
- [phrasenets](https://phrasenets.news-r.org) - Create phrase networks

## Installation

You can install newsr from Github with remotes:

```r
# install.packages("remotes")
remotes::install_github("news-r/newsr")
```

Loading newsr essentially loads all packages in the environment.

```{r}
library(newsr)
```

The only function currently available is to check which API keys as set, or in other words, which APIs (packages) the user may call.

```{r}
check_keys()
```

Please note that the 'newsr' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.